The Driving Forces Behind API Evolution

### 2015-05-20 thesis/paper.tex
Removed RQ3

\subsection{Research Questions} \label{rqs}
\begin{description}
\item[\textbf{RQ1}] How do companies actively drive API evolution?
\item[\textbf{RQ2}] How do APIs ``passively'' evolve?
\item[\textbf{RQ3}] To what extent can we reverse engineer API change decisions?

@@

\section{Methodology} \label{methodology}
%Intro and summary
This study has been conducted using the case study methodology \cite{runeson2009guidelines}. Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis. The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context. The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case, runeson2009guidelines, yin2013case, robson2002real}. An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}. An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ3}.

@@

%RQ1
The trends identified previously were then classified according to the software maintenance types \cite{chapin2001types}. The process followed the decision tree used for classifying the types of software evolution and software maintenance \cite{chapin2001types}. Each of the previously identified trends were given a main type of maintenance and, if appropriate, a secondary type. This material, as well as the results of the interview, were then used as the basis for answering \textbf{RQ1}.

%RQ2
The analysis of the changes and trends, combined with the information gathered from the interview, allowed us to answer \textbf{RQ2} by determining if Lehman's Laws apply to the changes made to the API.

%RQ3
To allow us to answer \textbf{RQ3}, we compared our analysis and interpretation of the trends identified prior, against what was expressed by the API architect, during the interview. Success was determined by comparing the inter-rater reliability, by calculating Cohen's kappa \cite{cohen1968weighted} for the gathered data.

@@

\subsubsection{Types 1by1}

@@

\subsubsection{Laws 1by1}

@@

\subsection{RQ3 Results}
\noindent
RQ3: \textbf{To what extent can we reverse engineer API change decisions?}
\smallskip

>>>>

\subsection{Research Questions} \label{rqs}
\begin{description}
\item[\textbf{RQ1}] What are the driving forces to API evoltion?
\item[\textbf{RQ2}] To what extent can we reverse engineer API change decisions?

@@

\section{Methodology} \label{methodology}
%Intro and summary
This study has been conducted using the case study methodology \cite{runeson2009guidelines}. Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis. The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context. The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case, runeson2009guidelines, yin2013case, robson2002real}. An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}. An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ2}.

@@

%RQ1
The trends identified previously were then classified according to the software maintenance types \cite{chapin2001types}. The process followed the decision tree used for classifying the types of software evolution and software maintenance \cite{chapin2001types}. Each of the previously identified trends were given a main type of maintenance and, if appropriate, a secondary type. In addition to this, we analysed the trends based on Lehman's Laws, to determine if they applied to the changes made to the API. This material, as well as the results of the interview, were then used as the basis for answering \textbf{RQ1}.

%RQ2
To allow us to answer \textbf{RQ2}, we compared our analysis and interpretation of the trends identified prior, against what was expressed by the API architect, during the interview. Success was determined by comparing the inter-rater reliability, by calculating Cohen's kappa \cite{cohen1968weighted} for the gathered data.

@@

\subsubsection{Types of Change}

@@

\subsubsection{Lehman's Laws}

@@

\subsection{RQ2 Results}
\noindent
RQ2: \textbf{To what extent can we reverse engineer API change decisions?}
\smallskip
